---
title: "TENISDATA Assignment"
author: "Bilgehan Kıran Çelebi"
date: "11/27/2019"
output: html_document
---

```{r}
library(tidyverse)
load("/Users/bilgehan.kiran/Documents/BilgeDersler/BigDataAnalytics/week11/atp_tennis_data_2017.RData")
```


# 1-Rank countries (flag codes) by the singles champions order

```{r}

champ_flags_df <- tourney_df %>% left_join(.,player_df, by =c("singles_winner_player_id"="player_id")) %>% count(flag_code, sort = TRUE) 

champ_flags_df
```



# 2-Rank countries which didn't get any singles championships by the genres won when they win the match 

```{r}
nonchamp_players <- player_df  %>% select(player_id, flag_code) %>% anti_join(.,champ_flags_df)

nochamp_winn_player <- nonchamp_players %>% left_join(.,score_df, by=c("player_id"="winner_player_id")) 

nochamp_winn_player %>%  group_by(flag_code)  %>% summarise(total_wins=sum(winner_games_won,na.rm = T)) %>% arrange(desc(total_wins)) 
 

```

# 3-No championship winner players whose service points were better than the winner of their matches

```{r}
nochamp_match_id <- inner_join(nonchamp_players,score_df, by=c("player_id"="loser_player_id")) %>% select(player_id,match_id ) 

player_better_in_service <- inner_join(nochamp_match_id , stats_df) %>% select(player_id,winner_service_points_won, loser_service_points_won) %>% filter(winner_service_points_won < loser_service_points_won)


player_info <- inner_join(player_better_in_service, player_df) %>% distinct(player_id,first_name, last_name, flag_code,birth_place)

player_info

```

We can see the information about 82 players who had better service points in the matches they had.


# 4- rank of the countries which had least match winner 

```{r}
champ_winner_players <- score_df %>% left_join(.,player_df, by=c("winner_player_id"="player_id")) 

champ_winner_players %>%  group_by(flag_code)  %>% count()  %>% arrange(n) 


```

As we can see sadly TR is one of the countries who had least match winner. 
